### 2012-03-21 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

>>>>

\subsection{Example}
\begin{lstlisting}[float, caption=Sample query 2., frame=single, label=listing_sample_query_2]
for $p in /site/people/person
let $a :=
  for $t in /site/closed_auctions/closed_auction
  where $t/buyer/@person = $p/@id
  return $t
return <item person="{$p/name/text()}">{count($a)}</item>
\end{lstlisting}

\begin{figure}
\label{FIG_syntax_tree_2}
\caption{Sample syntax tree 2.}
\includegraphics[scale=0.7]{syntax_tree_2.eps}
\end{figure}

Figure \ref{FIG_syntax_tree_2} shows the syntax tree of the query in Listing \ref{listing_sample_query_2}. In this tree, the algorithm founds one occurrence of the join pattern 3. The two for clauses and one where clause which form the occurrence are shown in the red boxes.

The next phase marks this occurrence as (O1) case with weight 0.5 and the following statements are inferred:

\begin{itemize}
\item Key $k = (/site/people/person, \{@id\})$ is satisfied.
\item Foreign key $((/site/closed\_auctions/closed\_auction, \{buyer/@person\}) \rightarrow k)$ is satisfied.
\item Key $(/site/closed\_auctions/closed\_auction, \{buyer/@person\})$ is not satisfied.
\end{itemize}
